%--------------------------------------------------------------------------------------
%%% hlavná stránka

\begin{titlepage}

\begin{center}

{\sc\LARGE University of Žilina}

\medskip

{\sc\Large Faculty of Management Science and Informatics}

\vfill\vfill\vfill\vfill

{\sc\LARGE Master's thesis}

\smallskip

{\large Field of study: {\bf Information systems}}

\end{center}

\vfill\vfill\vfill

\begin{center}
    
{\large\bf Jozef Chmelár}

\smallskip

{\large\bf Application of blockchain technology}

\smallskip

Tutor: {\bf Ing. Michal Kvet, PhD. }

\smallskip

Registration number : 760/2018	

\smallskip

ŽILINA 2019

\end{center}

\end{titlepage}

%--------------------------------------------------------------------------------------
%%% cestne vyhlásenie

\pagebreak
\hfill
\vfill

\begin{center}

\sc\Large\textbf{Declaration}

\end{center}

I hereby declare that this thesis was written by myself. I also declare that all the sources and information used  to complete the thesis are included in the list of references

\vspace{1em}

I agree with publication of this thesis.

\vspace{2em}

In Žilina, 2. May 2019    \hfill ...........................

\hfill Jozef Chmelár \hspace{0,5em}

% \vfill
% \hfill
\pagebreak

%--------------------------------------------------------------------------------------
%%% poďakovanie

\pagebreak
\hfill
\vfill

\begin{center}

\sc\Large\textbf{Acknowledgement}

\end{center}

I'd like to thank to my supervisor Ing. Michal Kvet, PhD . for his professional help, feedback and always pointing me to the right direction.

\vspace{2em}

In Žilina, 2. May 2019  \hfill ...........................

\hfill Jozef Chmelár \hspace{0,5em}

\pagebreak

%--------------------------------------------------------------------------------------
%%% slovensky abstrakt

\pagebreak

\begin{center}

\sc\Large\textbf{Abstrakt}
    
\end{center}

\noindent
{\sc CHMELÁR Jozef:} {\em Využitie technológie blockchain}
[Diplomová práca] 

\noindent
Žilinská univerzita v Žiline,  
Fakulta riadenia a informatiky,  
Katedra informatiky

\noindent  
Vedúci práce - Ing. Michal Kvet, PhD . Stupeň odbornej kvalifikácie - Inžinier.- Žilina: FRI ŽU v Žiline, 2018 - Počet strán \pageref{LastPage}
\noindent 



\vspace{1em}

Cieľom diplomvej práce je analýza technológie blockchain, jej použitie a súčasné implementácie. Vytvorenie aplikácie ktorá využíva blockchain na ukladanie výrobných dát. Tieto dáta musia byť uložené v nemennom stave aby poskytovali dôkaz o výrobe a zachovali integritu dát.

\vspace{1em}

\noindent
{\bf Kľúčové slová:} Blockchain, decentralizovaná databáza

\pagebreak

%--------------------------------------------------------------------------------------
%%% anglicky abstrakt

\selectlanguage{english}

\pagebreak

\begin{center}

\sc\Large\textbf{Abstract}
    
\end{center}

\noindent
{\sc CHMELÁR Jozef:} {\em Application of blockchain technology
}
[Master´s thesis] 

\noindent
University of Žilina,  
Faculty of Management Science and Informatics,  
Department of Informatics

\noindent  
Supervisor: Ing. Michal Kvet, PhD .  - Qualification level : Masters.- Žilina: FRI ŽU in Žilina ,2018 - Number of pages: \pageref{LastPage} 


\vspace{1em}

Thesis should analyze blockchain as a technology, its usage and current implementations. The goal is to develop a blockchain application for storing manufacturing data. This data should be stored in immutable state to provide proof of manufacturing and integrity of data.

\vspace{1em}

\noindent
{\bf Keywords:} Blockchain, decentralized database

\pagebreak

\selectlanguage{english}